### 2011-05-12 paper.tex
editted some text at the beginning of the amplify section

Initially, this may seem to be obviously true for the same reasons that $\bp \cdot \p = \strongbp \cdot \p$. The problem is that amplification requires running some machine which accepts a language in $C$ more than once. This requires the structure of $C$ to allow for such repetitions. In particular, we will find that it is nontrivial when the $\parity$ operator is involved. This brings us to the concept of majority reductions.
\begin{definition}\label{defmajority}
We say that a complexity class $C$ is \emph{closed under majority reductions} if for any partial function $f \in C$, the partial function $\majority(f)$ defined by
$$\majority(f)(\langle x_1, \ldots, x_k\rangle) = 
\begin{cases}1 & \text{ if the number of $i$ such that }f(x_i) = 1\text{ is at least $\frac{k}{2}$} \\
0 & \text{ if the number of $i$ such that }f(x_i) = 0\text{ is more than $\frac{k}{2}$}\\
\x & \text{ otherwise}
\end{cases}$$
is in $C$.
\end{definition}
Now, we see that majority reductions are exactly what we want for amplification:
\begin{lemma}\label{majorityimpliesamplify}
If $C$ is a complexity class which is closed under majority reductions and polynomial time reductions, then \emph{$f\in\strongbp \cdot C$.}
\end{lemma}
\begin{proof}
This is now the same application of the Chernoff bound which shows that $\bp \cdot \p = \strongbp \cdot \p$. Suppose $f$ is a partial function in $\bp \cdot C$. Then there is a partial function $g$ in $C$ such that $\pr_y [g(\langle x,y\rangle) = 1] > 2/3$ if $f(x) = 1$ and $\pr_y [g(\langle x, y\rangle) = 0] > 2/3$ if $f(x) = 0$, where the length of $y$ is equal to $p(|x|)$ for some polynomial $p$. Let $q$ be a polynomial, where $e^{-q(|x|)}$ is the desired error probability. Let $k = 48q(|x|)$.

@@

>>>>

Initially, this may seem to be obviously true for the same reasons that $\bp \cdot \p = \strongbp \cdot \p$. The problem is that amplification requires running some machine which accepts a language in $C$ more than once. This requires the structure of $C$ to allow for such repetitions. In particular, we will find that it is nontrivial when the $\parity$ operator is involved. The fact that we need $C$ to be well-structured rather than just any $\{\Sigma, \Pi, \bp, \parity\}$-constructible class is due to an annoying detail that will come up when we deal with oracles in Section \ref{oracle}. We will cover the non-well-structured case in Section \ref{notwellstruct}.

To show that a class is amplifiable, we need the concept of a majority reduction.
\begin{definition}\label{defmajority}
We say that a complexity class $C$ is \emph{closed under majority reductions} if for any partial function $f \in C$, the partial function $\majority(f)$ defined by
$$\majority(f)(\langle x_1, \ldots, x_k\rangle) = 
\begin{cases}1 & \text{ if the number of $i$ such that }f(x_i) = 1\text{ is at least $\frac{k}{2}$} \\
0 & \text{ if the number of $i$ such that }f(x_i) = 0\text{ is more than $\frac{k}{2}$}\\
\x & \text{ otherwise}
\end{cases}$$
is in $C$.
\end{definition}
Now, we see that majority reductions are exactly what we want for amplification:
\begin{lemma}\label{majorityimpliesamplify}
If $C$ is a complexity class which is closed under majority reductions and polynomial time reductions, then \emph{$f\in\strongbp \cdot C$.}
\end{lemma}
\begin{proof}
This is now the same application of the Chernoff bound which shows that $\bp \cdot \p = \strongbp \cdot \p$. Suppose $f$ is a partial function in $\bp \cdot C$. Then there is a partial function $g$ in $C$ such that $\pr_y [g(\langle x,y\rangle) = 1] > 2/3$ if $f(x) = 1$ and $\pr_y [g(\langle x, y\rangle) = 0] > 2/3$ if $f(x) = 0$, where the length of $y$ is equal to $p(|x|)$ for some polynomial $p$. Let $q$ be a polynomial, where $e^{-q(|x|)}$ is the desired error probability. Let $k = 48q(|x|)$.

@@

\section{The non-well-structured case}\label{notwellstruct}
